---
title: "Tooth Growth"
author: "Daniel Jungen"
date: "23 November 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## ToothGrowth dataset

According to https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/ToothGrowth.html the ToothGrowth dataset is described as follows:

"The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, (orange juice or ascorbic acid (a form of vitamin C and coded as VC)."

It is formatted as follows:

"A data frame with 60 observations on 3 variables.

[,1] 	len 	numeric 	Tooth length

[,2] 	supp 	factor 	Supplement type (VC or OJ).

[,3] 	dose 	numeric 	Dose in milligrams/day "


First we should check the different levels in the variables "supp" and "dose":

```{r}
unique(ToothGrowth$supp)

unique(ToothGrowth$dose)

```

As stated in the description we see two different levels of supplement types (OJ and VC) and we also see three different doses (0.5, 1.0 and 2.0).

The interesting questions in that context are

1. Does the supplement type have an influence on the tooth length?

2. Does the dose have an influence on the tooth length?


First we calculate the mean of the tooth length per supplement type:

```{r}
aggregate(ToothGrowth[,1], list(ToothGrowth$supp), mean)
```

And now the mean of the tooth length per dose:

```{r}
aggregate(ToothGrowth[,1], list(ToothGrowth$dose), mean)
```

The means suggest that the orange juice is the better supplement for bigger teeth and the higher the dose the bigger the teeth.

# Test 1: Does orange juice lead to bigger teeth?

$H_0=\text{OJ leads to bigger teeth vs. } H_1 = \text{OJ does not lead to bigger teeth}$


# Test 2: A higher dose of vitamin c leads to bigger teeth?

$H_0=\text{A higher dose of vitamin c leads to bigger teeth vs. } H_1 = \text{A higher dose of vitamin c does not lead to bigger teeth}$